---
title: "R-Visualization for qqplot2"
author: "許sir"

---


### Data Description
#### [第一組範例]是內建資料集 Diamonds。~54,000 round diamonds from http://www.diamondse.info/
#### [第二組範例]是內建資料集 WorldPhones。

### [設定所需的函式庫(libraries)以及載入資料]
```{}
install.packages("ggplot2")
install.packages("ggplot2movies")
```

```{r message=FALSE, warning=FALSE, results='hide'}
library(ggplot2)
library(reshape2)
library(ggplot2movies)

data(diamonds) #第一組data
data(WorldPhones) #第二組data
data(movies)  #第三組data

ggplot(data=diamonds, aes(x=cut)) + geom_bar() #a quick example 
```

## PART 1.三大圖型概述

#### [畫圖基本概念]你要決定到底是要Factor or Numeric?

### [第一大類] bar plot
```{r message=FALSE, warning=FALSE}
str(diamonds)
head(diamonds)
summary(diamonds)
```

```{r message=FALSE, warning=FALSE}
ggplot(data=diamonds, aes(x=cut)) + geom_bar() #x must be of type factor

ggp <- ggplot(data=diamonds[1:5,], aes(x=cut)) + geom_bar() #geom_bar drops category with no occurrence
ggp

ggplot(data=diamonds, aes(x=cut)) + geom_bar() + coord_flip() #horizontal bar


ggp <- ggp + xlab("Cut") + ylab("Count") + ggtitle("Hello ggplot!") #change label naming
ggp

ggp + geom_bar(fill="snow", color="black") # change color and see colors() if you're picky

```

### 1-1.我們可以事先做一點點計算(plot counts as is )
```{r message=FALSE, warning=FALSE}
diamonds_precounted <- as.data.frame(table(diamonds$cut, dnn=c("Cut")))
diamonds_precounted

ggplot(diamonds_precounted, aes(x=Cut, y=Freq)) + geom_bar(stat="identity") # default is "bin"
```


### 1-2.有關於stat=“identity”
#### A.row should be unique: otherwise counts will be summed up
#### B.missing label will be present at default: differ from stat="bin"
#### C.negative bar is allowed

```{r message=FALSE, warning=FALSE}
diamonds[1:5,]
ggplot(diamonds[1:5,], aes(x=cut, y=depth)) + geom_bar(stat="identity")

ggplot(diamonds_precounted, aes(x=reorder(Cut, -Freq), y=Freq)) + 
  geom_bar(stat='identity') # The order is determined by factor levels
```

### 1-3.stack grouping 
```{r message=FALSE, warning=FALSE}
ggplot(data=diamonds, aes(x=color, fill=cut)) + geom_bar() #by fill
ggplot(data=diamonds, aes(x=color, color=cut)) + geom_bar() #by color
ggplot(data=diamonds, aes(x=color, fill=cut)) + geom_bar(position="dodge") #dodge grouping

```

### 1-4.From bar to histogram 
#### when x is numeric
```{r message=FALSE, warning=FALSE}
ggplot(data=diamonds, aes(x=price)) + geom_bar()
ggplot(data=diamonds, aes(x=price, fill=cut)) + geom_bar(position="stack") #by stack
ggplot(data=diamonds, aes(x=price, fill=cut)) + geom_bar(position="identity", alpha=.5) #by identity (overlapping)

ggplot(data=diamonds, aes(x=price, fill=cut)) + geom_density(position="identity", alpha=.5) #from histogram to density plot

ggplot(data=diamonds[diamonds$cut %in% c("Fair", "Ideal"),], aes(x=price, fill=cut)) + 
    geom_density(position="identity", alpha=.5) + 
    geom_bar(position="identity", alpha=.5) #both histogram and density (scale wrong?K)


```

### [第二大類] Line Graph

```{r message=FALSE, warning=FALSE}
head(WorldPhones) #第二組data基本概述
str(WorldPhones)

#Remember: ggplot eat only data.frames
WorldPhones.DF <- as.data.frame(WorldPhones)
WorldPhones.DF$year <- rownames(WorldPhones.DF)
class(WorldPhones.DF) # this time we should be fine!

```

### 2-1.比較一下這兩種方法有什麼不同
```{r message=FALSE, warning=FALSE}
ggplot(WorldPhones.DF, aes(x=year, y=Asia)) + geom_line(size=1.5)
ggplot(WorldPhones.DF, aes(x=as.numeric(year), y=Asia)) + geom_line(size=1.5)
```

### 2-2.長表與寬表之轉換
```{r message=FALSE, warning=FALSE}
WP=WorldPhones.DF[,c(1:3,8)]
head(WP,8) #Wide format


WP.long=melt(WP,id.vars='year') # ?Hmelt?N?????ഫ??Long Format?A?Hid.vars?O?d????
colnames(WP.long)= c('Year','Region','Value')
head(WP.long) #Long format with melt


```

### 2-3.各種Line的不同
```{r message=FALSE, warning=FALSE}
WP.long$Year <- as.integer(as.character(WP.long$Year))
ggplot(WP.long, aes(x=Year, y=Value, color=Region)) + geom_line(size=1.5)

ggplot(WP.long, aes(x=Year, y=Value, linetype=Region))+
  geom_line(size=1.5)

ggplot(WP.long,aes(x=factor(Year), y=Value))+
  geom_line(aes(linetype=Region,group=Region),size=1.5)

ggplot(WP.long, aes(x=Year, y=Value, linetype=Region)) + geom_line(size=1.5) +
  guides(linetype=guide_legend(reverse=TRUE))


```

### [第三大類] Scatter Plot
```{r message=FALSE, warning=FALSE}
head(movies) #第三組data基本概述
str(movies)

movies1 <- movies[!is.na(movies$budget),]
ggplot(movies1, aes(x=budget, y=rating)) + geom_point()
```

### 3-1.控制point的各種型態
```{r message=FALSE, warning=FALSE}
ggplot(movies1, aes(x=budget, y=rating)) + geom_point(shape=5, size=3)

```

### 3-2.Grouping
```{r message=FALSE, warning=FALSE}
ggplot(movies1, aes(x=budget, y=rating, color=Action)) + geom_point() #Grouping: by binary variable

ggplot(movies1, aes(x=budget, y=rating, color=factor(Action))) + 
    geom_point() + labs(color='Action Movie?') #Grouping: by categarical variable

ggplot(movies1, aes(x=budget, y=rating, color=factor(Action), shape=(length > 120))) + 
    geom_point(size=3) + labs(color='Action Movie?') #Multi-grouping
```

### 3-3.regression line
```{r message=FALSE, warning=FALSE}
ggplot(movies, aes(x=votes, y=rating)) + geom_point() +
    stat_smooth(method=lm, level=.95) # add se=FALSE to disable CI

ggplot(movies, aes(x=votes, y=rating)) + geom_point() + stat_smooth() #The default is a polynomial fit

ggplot(movies1, aes(x=budget, y=rating, color=factor(Action))) + 
    geom_point() + labs(color='Action Movie?') + stat_smooth(method=lm, se=FALSE) #Fitting is smart to align with grouping


```

## PART 2.基本統計運算

### 2-1-1. Which Type of Film Cost the Most in Average?
```{r message=FALSE, warning=FALSE}
movietype <- colnames(movies)[18:24]
movies1_singletype <- movies1[rowSums(movies1[, movietype]) == 1,] # remove multi-typed
movietype_alt <- c(movietype[length(movietype)], movietype[-length(movietype)]) 
# convert multiple dummies into one factor as grouping var
# a little matrix operation will do the trick
dummies <- as.matrix(movies1_singletype[, movietype_alt])
movies1_singletype$Type <- factor(dummies %*% (1:length(movietype_alt)), labels=movietype_alt)

# Compute the Average Budget of Each Type
tapply(movies1_singletype$budget, movies1_singletype$Type, mean)
```

### 2-1-2. Determine the variation
```{r message=FALSE, warning=FALSE}
#The first factor level of movietype, Short, is represented as the intercept term.
lmfit <- lm(as.formula("budget ~ Type"), movies1_singletype)
summary(lmfit)$coef 

```

### 2-1-3. Another way to estimate the coefficients
```{r message=FALSE, warning=FALSE}
#The last predictor, Short is combined into the intercept term.
# mean(movies1_singletype[movies1_singletype$Animation == 1, 'budget'])
lmfit <- lm(as.formula(paste('budget ~', paste(movietype, collapse=' + '))), 
            movies1_singletype)
summary(lmfit)$coef
```

### 2-1-4. Draw the regression lines of each type
```{r message=FALSE, warning=FALSE}
#What is the association between cost and rating, conditional on type?

movies1_reg_plot <- ggplot(movies1_singletype, aes(x=budget, y=rating, color=Type)) + 
  geom_point(shape=1) +
  
  # set fullrange=T will extend the fitted line outside the sample range
  stat_smooth(method=lm, se=FALSE, fullrange=FALSE, size=1.5) +
  
  # color is the grouping interface, hence scale_color_*
  scale_color_discrete(name='Movie Type: # of samples', 
                       labels=paste(levels(movies1_singletype$Type), ': ', 
                                    table(movies1_singletype$Type)))
```

### 2-1-5.Output
```{r message=FALSE, warning=FALSE}
movies1_reg_plot
```

